Modelling last glacial cycle ice dynamics in the Alps

### 2017-09-12 articles/cycle/alps-cycle.tex
Draft discussion of flow patterns.

    \begin{itemize}
    \item Maximum stages flow pattern is complex (Fig.~\ref{fig:lgmvel}a).
    \item Flow goes sometimes across topography (Fig.~\ref{fig:lgmvel}a).
    \item Transfluences (Montgenèvre, col de l'Échelle, Simplon, Albrun, Gries,
                        (Brünig, Majola, Tagliamento)
    \end{itemize}

>>>>

    The modelled flow pattern at 24.56\,ka is complex (Fig.~\ref{fig:lgmvel}a).
    The modelled fast-flow regions generally occur along the main river
    valleys, while ice domes and ice divides are predominantly located over
    major reliefs . Nevertheless, the model results depict occasional ice flow
    across mountain passes (transfluences) and ice divide above topographic
    lows.

    Major transfluences occur for instance across col du Mont-Cenis,
    Simplonpass, Brünigpass in the western Alps, and over Fernpass,
    Gailbergsattel and Stranigeralpe in the Eastern Alps
    (Fig.~\ref{fig:lgmvel}a). Finally, self-sustained ice domes characteristic
    of ice caps are modelled in two locations over Flüelapass and Ötztal
    (Fig.~\ref{fig:lgmvel}a).

    In the Eastern Alps, modelled transfluences and crosswise divides are
    generally incompatible with geological reconstructions, indicating that
    climate deterioration was overestimated in the model input. In the Western
    Alps, however, transfluences generally occur where they have been
    documented by geologic evidence. These model results depict the LGM Alpine
    ice complex as an intermediate between ice fields and ice caps, bearing
    characteristics of both and perhaps no modern analogue.

    \todo{look for references, add location names on Fig.~\ref{fig:lgmvel}.}
